Predicting sales of newly published books

### 2015-08-25 paper.tex
Revisa intro y términos

% A partir de datos históricos de tiradas editoriales se plantea el
% uso de varios modelos para la clasificación y predicción de la
% tirada de nuevos títulos editoriales.

A company that intends to release a new product has a high risk due to
the complexity of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

In the field of publishing industry, the challenge is to print an
adequate number of copies but not too much, as the unsold volumes will
lead to losses, whereas if the number of printed copies was not
enough, you can always print more. 
Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. 
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. %publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
% Antonio propone traducirlo como "print run". Lo pongo así.

>>>>

Publishing a book, as releasing any other product, implies several
types of risks and costs due to
the complexity and expenses of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product is also new to the company, and sales forecasts can
only be based on the experience of similar products. 
In this scope, having accurate estimates of future sales of the new
product is extremely important \cite{ChingChin2010} so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sale predictions 
(a reduction of forecasting errors) results in an improvement in the 
production \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

Book publishers, as well as other content producers, release new {\em
  products} more frequently than other industries and thus face the
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, whereas if the number of printed copies was not
enough, you can always print more. In this sense, errors in one or the
other direction do not have the same importance, although a temporal
scarcity of a book that is selling well is also a problem.

Thus, it is extremely important using predictive tools to optimize 
production and improve the publishing company profits or minimize losses \cite{Zhao2001}
by forecasting the sales a new book might achieve. This is the
objective we have in this paper.
An example is the optimization of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. %publishing roll.  
% [Pedro] "publishing roll" es como he encontrado "tirada editorial" traducido...
% Antonio propone traducirlo como "print run". Lo pongo así.
